Verifying Demonstrations

### 2020-02-25 paper/DBSchnorr-n-bit.tex

We wanted to formally verify the protocol security properties. To realize this, 
we used the Tamarin prover~\cite{meier2013tamarin}. Tamarin does not include 
originally the possibility to reason on time and space in its model.
However, thanks to a recent work by \textcite{TamarinDB}, all the common 
properties mentioned in the previous subsection can be equivalently 
characterized with a causality-based definition relying only on the order of 
messages.

The whole Tamarin code we wrote is provided in \cref{apdx:tamarin-spec}, with a short discussion of the modeling choices that we have made. 
It contains a specification of the distance-bounding protocol described previously, a definition of the soundness and correctness properties that ensure the protocol actually produces the expected result, and a definition of the security properties we want to ensure.

Tamarin's auto-prover validated the soundness and correctness properties (in negligible computation time) but does not terminate when trying to prove the security properties.
This means that no trace violating the security properties is found, but the prover cannot conclusively validate that the desired properties are true. 
We are currently investigating the Tamarin interactive mode to validate as well the security properties.

>>>>

We formally verify the protocol security properties using the Tamarin
prover~\cite{meier2013tamarin}. Tamarin does not originally include
the possibility to reason on time and space in its model.  However,
thanks to a recent work by \textcite{TamarinDB}, the common properties
can be equivalently characterized with a causality-based definition
relying only on the order of messages.

The whole Tamarin code we wrote is provided in \cref{apdx:tamarin-spec}, with a short discussion of the modeling choices that we made. 
It contains a specification of the distance-bounding protocol described previously, a definition of the soundness and correctness properties that ensure the protocol actually produces the expected result, and a definition of the security properties we want to ensure.

Tamarin's auto-prover validated the soundness and correctness
properties (in negligible computation time) and proved the security
properties used in~\cite{TamarinDB}. In the meantime,
\textcite{TamarinDBTF} introduced the notion of post-collusion
security which enabled them to prove \ac{DBTF}. In future work, we
will use this extension on our protocol.

### 2020-02-25 paper/conclusions.tex

In this paper, we have introduced \CROCUS, a privacy-preserving protocol for verifiably counting participants at protests. 
Despite the verification, the privacy of the participants is preserved to the extent possible by their physical presence at the protest, with the following caveat. Given the conflict between verifiability and receipt-freeness when counting presence, any digital trace needed for verifiability could conceivably be used to substantiate a claim that was by itself weaker. For instance if there is auxiliary information that points to a person having participated in a protest, for example pictures at the event, with face recognition and subsequent identification, IP address of the person's home router, etc., then any remaining uncertainty from false positives could be reduced by learning from data on the ledger and the person's smartphone. This potential difference can thus be considered the price for verifiability. Against an attacker without such side information, \CROCUS preserves the participants' privacy, expressed in terms of unlinkability to their identity and between events.

%To achieve that, we adapted the Schnorr protocol to develop distance-bounding anonymous credentials. \sonja{Rephrase the following after we have requirements and results:
%Except for receipt freeness, which we cannot guarantee if the adversary gets access to Alice's device and secret PRF key after her participation has been witnessed and before she had a chance to delete it, \CROCUS fulfills all verification and privacy properties we derived from those of electronic voting complemented by the specific constraints on time and location required for protests. }
%With respect to privacy, \CROCUS provides anonymity (of participants)  and unlinkability (between protests) unless the adversary gets access to the private key/ID or has side information (she also needs the private key for proof of the cause (cid) supported by the protester, otherwise she does not learn more than without \CROCUS).
\sonja{update sec analysis results}

%Of separate interest, we have also built distance-bounding protocols for authenticating more general attributes than provided by previous \ac{DB} ones.
%All privacy-preserving \ac{DB} protocols have so far focused on identity-based authentication, but not authentication of general attributes, as is the case for anonymous credentials.
%With our contribution, Alice can now prove more complex statements to Bob, (\eg  that she is older than 18 but younger than 40 without revealing her actual age) and at the same time Bob can be sure that Alice is not just relaying messages from her older sister Carol.

% In general, none of the related works fulfills the eligibility
% verifiability (one proof per person, temporal and spatial eligibility ---
% \cref{%
%   CountOnce,%
%   TemporallyRelated,SpatiallyRelated,%
% }).
% To some extent, some techniques do fulfill designated event (\cref{DesignatedEvent}), since people usually use placards in the protests.
% Also, some schemes provide universal verifiability (\cref{UniversalVerif}), but not individual verifiability (\cref{IndividualVerif}).
% Moreover, if they provided individual verifiability, they would likely violate 
% the privacy requirements --- if people must recognize themselves in photos, 
% others can recognize them too.
% Finally, most of the current methods are estimates, with quite some error margins. 
While \CROCUS is an actual count and not an estimate, its accuracy for the total number of participants hinges on the participants having the necessary equipment (\ie, a smartphone or similar device), some sort of trustworthy credential, and the willingness to run the protocol. 
Owing to the network effect, until used by most participants, \CROCUS would result in a considerable undercount. 
However, it represents a first step toward accurate verifiable yet privacy-preserving crowd counting by showing how it can be done in theory at least and in practice once some assumptions concerning hardware and e-identities become more realistic. 
While the necessary technologies are not yet available in most authoritarian regimes, some of them are in several democracies. We believe that it is important to implement systems such as ours also there to support the maintenance of democratic processes and counter fake news.

>>>>

In this paper, we have adapted the Schnorr protocol as a
distance-bounding protocol.  It allows to construct distance-bounding
general attribute-based authentication, more general attributes than
provided by previous \ac{DB} ones.  With our contribution, Alice can
now prove more complex statements to Bob; \eg that she is older than
18 but younger than 40 without revealing her actual age, and at the
same time Bob can be sure that Alice is not just relaying messages
from her older sister Carol.

### 2020-02-25 paper/related-work.tex
removes .DS_Store, reinstates conclusions and related work from crocus with only relevant parts included

\subsection{Distance bounding}

One protocol exists in the literature that provides \acp{PPK} with most of the 
desired properties described previously, ProProx~\cite{ProProx}\footnote{Note 
  that~\cite{ProProx} uses the abbreviation PoPoK, we prefer \acs{PPK} for 
  shorter notation.}.
ProProx is secure against a malicious verifier, but it provides \iac{PPK} protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = 
  \alpha^2]\)), while in our context, we need \iac{PPK} protocol for discrete 
logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\), see \cref{ZK-anon-cred} for 
details).
To realize this, we will now introduce such a protocol to enable us to have 
\ac{DB} anonymous credentials.

\subsection{Crowd counting methods}
\input{crowd-counting-methods.tex}

\subsection{Location proofs}
\input{location-proofs.tex}

>>>>

One protocol exists in the literature that provides \acp{PPK} with most of the desired properties described previously, ProProx~\cite{ProProx}\footnote{Note that~\cite{ProProx} uses the abbreviation PoPoK, we prefer \acs{PPK} for shorter notation.}.
ProProx is secure against a malicious verifier, but it provides \iac{PPK} protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = 
  \alpha^2]\)), while in our context, we need \iac{PPK} protocol for discrete logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\)) due to our choice of anonymous credentials whose desirable properties we list in \cref{ZK-anon-cred}.%, which in turn is due to their \ac{PRF} for deriving identifiers from a long-term ID with unlinkability to the original ID but with proof of validity of this derivation.

% One protocol exists in the literature that provides \acp{PPK} with most of the 
% desired properties described previously, ProProx~\cite{ProProx}\footnote{Note 
%   that~\cite{ProProx} uses the abbreviation PoPoK, we prefer \acs{PPK} for 
%   shorter notation.}.
% ProProx is secure against a malicious verifier, but it provides \iac{PPK} protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = 
%   \alpha^2]\)), while in our context, we need \iac{PPK} protocol for discrete 
% logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\), see \cref{ZK-anon-cred} for 
% details).
